A space-time skew-$t$ model for threshold exceedances

### 2016-05-30 LaTeX/response.tex

% \usepackage[left=1in,top=1in,right=1in]{geometry}
% \pdfpageheight 11in
% \pdfpagewidth 8.5in
% \linespread{2.0}
\input{mycommands.sty}
\begin{document}

\begin{center}
Point-by-Point response to Reviewer Comments\\
Biometrics MS \#150926M\\
\today
\end{center}

We wish to thank the associate editor and two reviewers for their thorough reviews and constructive suggestions.
To address the concerns raised in this review we have carefully edited the manuscript to clarify issues regarding the skew-$t$ parameterization and other notational issues.
We have also added some new simulation results to explore more complicated max-stable processes, and a discussion of the properties of the spatiotemporal extension of our model.
We hope you agree that these changes have improved the manuscript.

\section*{Response to the comments of the Associate Editor}
\subsection*{Major comments}
\begin{enumerate}[1.]
\item The model in (1) has a non-standard skew distribution notation. As far as I could check, the parameter $\sigma^2$ should have an inverse gamma with parameters $a = b$, and not arbitrary and different $a$ and $b$. The equality is important in the derivations and it is one of the reasons we get $2a$ degrees of freedom. Indeed, some reserachers adopt $a/2$ and $a/2$ (rather than $a$ and $b$) such that they end up with a degrees of freedom. Can you provide a web-supplement proof that your more general model with $a \neq b$ is a skew-$t$ distribution with $2a$ degrees of freedom, or provide a reference for this result?\\

\begin{response}
  \hl{DONE:}
  We have assumed that the errors $v(\bs)$ have unit variance, and $z \sim N(0, 1)$, so we require separate $a$ and $b$ so that $a$ can control the shape/degrees of freedom while $b$ controls the scale.
  Viewed this way, if $a = b$, then the degrees of freedom would determine the scale which is clearly too restrictive.
  To help clarify this, we have slightly modified the parameterization so that the degrees of freedom are $a$, and added additional clarification of the role of $b$ in Section \ref{s:skewt}.
  We have also added \ref{a:otherparams} to demonstrate our more general model with $a \neq b$ is a skew-$t$ distribution with $a$ degrees of freedom.
\end{response}

\item In the simulations, you adopted a prior distribution for the $a$ and $b$ parameters in $\sigma_t^2 (\bs) \sim IG(a, b)$ as $a \sim $Gamma$(0.1, 0.1)$ and $b$ with a discrete distribution over a mesh from 0.1 to 10 with spacing $0.1$. The parameter $\sigma_t^2(\bs)$ is clearly a crucial parameter as it controls the scale. Why this choice? Trial and error? What have you used in the real dataset? Is this supposed to be a default choice?\\

\begin{response}
  \hl{DONE:}
  There was actually a typo in the manuscript as submitted.
  The priors for $a$ and $b$ were inadvertently switched, so $a$ should have had a discrete distribution over a mesh from 0.1 to 10 with spacing $0.1$, and $b \sim $Gamma$(0.1, 0.1)$.
  With the reparameterization given in the response to Major Comment 1, this actually means that the prior for $a$ is now a discrete distribution over a mesh from 0.2 to 20 with spacing $0.2$.
  As we now clarify in the specification of these priors, $a$ is the scale-free shape parameter, and so this prior should be uninformative in all application.
  In contrast, $b$ is a precision parameter, so it's prior should be adapted to the scale of the response.
  In the real data analysis, we use the same discrete prior as in the simulation study, and find that for all settings in the cross validation, the posterior mean of $a$ is less than 3.
\end{response}

@@

\item A very confusing issue for me was the adoption of the new parametrization $\lambda = \lambda_1 \lambda_2$. Typically, users adopt a prior such as $\lambda \sim N(0,V)$ with a large and known value for $V$. One consequence is that the posterior distribution of $\lambda$ has non negligible probability mass around 0, making the skew model irrelevant. When you adopted the parametrization $\lambda = \lambda_1 \lambda_2$, you ``solved'' this issue by making zero an impossible value under the prior. The parameter $\lambda_1$ is equal to $−1$ or $+1$ and it basically selects the semi-axis where the slant parameter will live. The parameter $\lambda_2 \sim IG(a, b)$ and hence $\lambda_2 > 0$ and bounded away from zero, in practice. The value $\lambda = 0$ is not supported by the prior. Under your parametrization, you are artificially avoiding your model to become a simple gaussian process.

What, exactly, is the convergence problem you had with the $\lambda$ parameter before adopting this reparametrization?
It affected only $\lambda$?

Incidentally, you used the same notation $IG(a,b)$ for two different purposes: for $\lambda_2$ in page 10, and for $\sigma^2$ in page 4. Please, keep them different as there are a lot of things going on in your model.\\

\begin{response}
  \hl{DONE:}
  There was a typo in the manuscript submission, the prior on $\lambda_1$ should have been a discrete prior on $\{-1, 0, 1\}$ with probability of $1 / 3$ for each option.
  This was originally done to help with a computing issue when imputing the values below the threshold.
  The computing issue was fixed prior to the original submission, but we elected to use the $\lambda$ parameterization as originally presented.
  We have opted to use the parameterization in your suggestion where $\lambda \sim N(0, \sigma^2_\lambda)$.
\end{response}

@@

\item In page 6, section 3.1, you say that you ``impute the censored values as a step in the MCMC algorithm''. Why do you need these pseudo-values, specially considering that you do have the real below threshold observations? Is it because you need them follwoing to your tail model (the skew-$t$ model)? But why do you need all the uncensored pseudo data?

Anyway, you should make clear that trading a focus only on the extreme tail data you loose efficiency by decreasing the number of (real) data available. Censoring on purpose seems a rather drastic technique.\\

\begin{response}
  \hl{TODO:}
  This is a key argument in extreme value analysis which we realize we inadvertently took for granted.
  This is a rendition of the classic bias variance trade-off.
  A low threshold reduces variance by increasing the amount of data used to estimate parameters but risks inducing bias if the model is misspecified
  On the other hand, a high threshold mitigates potential bias because only the tails must be modeled.
  Therefore, by using a high threshold fewer precarious assumptions are required, but this increases variance by discarding data.
  For our fairly flexible skew-$t$ process, we found that a moderate threshold optimized this balance for both simulated and ozone data.
  Section \ref{s:censoring} now elaborates on this trade-off.
\end{response}

\item The temporal dependence structure is induced by putting AR(1) models on some of the skew-$t$ parameters.
It is not clear what sort of temporal dependence that induces on the data.\\

\begin{response}
  \hl{TODO:}
  Using simulated data, we have evidence to suggest that the model exhibits extremal dependence provided that the site $\bs$ is in the same partition for day $t$ and $t + 1$.
  However, we are unable to give a formal proof that our temporal construction maintains extremal dependence.
\end{response}
\end{enumerate}

\subsection*{Minor comments}
\hl{Unless otherwise stated, these are done}
\begin{enumerate}[1.]
  \item Page 3, line 11: ``\ldots with computing on the order of Gaussian models ''\\

  \begin{response}
    This has been corrected
  \end{response}

  \item Page 3, line 13: \ldots as well as TO make predictions \ldots \\

  \begin{response}
    This has been corrected
  \end{response}

  \item Page 3, line -2: \ldots compared TO Gaussian AND max-stable \ldots \\

  \begin{response}
    This has been corrected
  \end{response}

  \item Page 8, line -1: a partition in the $\bw^∗$ space induces a partition in the $\bw^∗$. The property (7) is used in the $\bw^∗$ space. Is this property still respected in the $\bw$ space since the transformation is non-linear and acts independently in each coordinate? \\

  \begin{response}
    When we create the partition, it is created in the space of the original data (i.e. using $\bw$).
    As you mention, because the transformation is non-linear and acts independently in each coordinate, the partition created using $\bw$ will be similar to, but not the same as the partition created using $\bw^*$.
    We have added clarification in Section \ref{s:temporal} to clarify that the partition is created in the $\bw$ space as opposed to the $\bw^*$ space.
    \hl{Is this something we should be concerned about?}
  \end{response}

  \item Page 9, line -5: ``the marginal distributions are Gaussian'': which distributions, those of $Y(\bs)$? \\

  \begin{response}
    Yes, we now clarify that we are referring to the distribution of $Y(\bs)$.
  \end{response}

  \item The hierarchical model in page 10 has $\sigma_t(\bs)$ multiplying only $v_t(\bs)$ and leaving out the term $|z_t(\bs)|$. I think this is a typo. \\

  \begin{response}
    This typo has been corrected.
  \end{response}

  \item In page 12, line -1: you mention the partition label switching problem appearing during the MCMC. This was not consequential for the inference? Can you expand on this? \\

  \begin{response}
    \hl{TODO:}
    In a spatial analysis, the primary objectives are to make spatial predictions and to estimate extreme probabilities.
    Both of these objectives are met by marginalizing over partition-specific parameters and are thus unaffected by label switching.
    We have added a comment to this effect in the MCMC description, and caution that label switching might be more concerning in other analyses.
  \end{response}

  \item There are several papers using skew distributions in the spatial context. You should refer to the most relevant ones in your related work section. \\

  \begin{response}
    \hl{TODO:}
    We have added several references given by Reviewer 2 to the introduction.
  \end{response}

@@

\end{enumerate}

\newpage
\section*{Response to the comments of the Reviewer 1}

\subsection*{Major comments}
\begin{enumerate}[1.]
  \item The overall modeling goal is never fully clear. In the abstract you write ``We present a new method based on the spatial skew-t process.'' But a new method for what? Reading the paper there are hints that you the aim of the modeling procedure might be to predict the probability of exceeding 75ppb (e.g. first line of the abstract), but this is then taken as one of your modeling thresholds (p.3 l.5--6; p. 15 l.5). In a new version of the paper, the modeling aims should be stated clearly upfront so that the results can be assessed against these aims. \\

  \begin{response}
    \hl{TODO:}
    As we now describe at the end of the first paragraph of the introduction, two objectives for our data analysis are spatial prediction and mapping the probability of an extreme event.
    In the extremes context, spatial prediction means using the values of monitored stations to determine whether an unmonitored site experienced an extreme event.
    Mapping the probability of extreme events could either be the marginal probability of an event, such as ozone exceeding 75ppb, or a map of an upper quantile, such as the map of the 99th percentile in Figure \ref{fig:ozoneq99}.
  \end{response}

  \item There is a lot of confusion about the ``threshold'', and what this means in various contexts. Sometimes you discuss this as fixed and specified by regulation (e.g. p.3 l.5) but other times you refer to the role of censoring as not allowing low-moderate values influence the fit (e.g. Section 3.1 or the stated goal of modeling ``spatial extremes'' in the first line of Section 3) even though you state that the constant threshold is not extreme everywhere (e.g. in the Abstract, and p.15 l.3 where in fact the highest threshold you use in the application is the 0.06 quantile at some sites, and so hardly the tail!). The role of the threshold needs to be much more clearly explained in the context of the application (fixed thresholds of interest), and modeling the extremes. \\

  \begin{response}
    \hl{TODO:}
    Yes, we can see how this could lead to confusion.
    In the revision, we now refer to the ``threshold'' as the value we select in the model-fitting process, i.e. $T$ in (\ref{eq:Yt}).
    We also bolstered the description of the trade-off involved in selecting $T$ (see AE comment 4) below (\ref{eq:Yt}).
    As mentioned in the response to the previous comment, we also want to compute probabilities of extreme events (e.g. ozone exceeding 75ppb).
    We now refer to this as the probability above a high \emph{level}, $L$.
    That is, we might use the data above threshold $T = 50$ppb in order to estimate the probability of the response exceeding level $L = 75$ppb.
    Of course, this is only reasonable if $L \ge T$, and the user is free to select the $T$ that gives the best estimate of this probability.
  \end{response}

  \item Section 3.2: you introduce a Poisson process as a device for allowing long range asymptotic independence. In fact, after its first mention on p.7 l.1 you never refer to a Poisson process again, but instead use a fixed number of knots, i.e. a uniform distribution. Amazingly this is not even commented on! The purpose of the Poisson process seems to be for the proof in Web Appendix C, so if spatial long-range independence relies on this feature (which, assuming a constant rate $\mu$ would eventually guarantee an incease in the number of points, as opposed to taking a fixed number of draws from a uniform distribution) then the discrepancies between these two assumptions ought to be thoroughly discussed. \\

  \begin{response}
    \hl{DONE:}
    Thank you for pointing out this important difference.
    Below ($\ref{eq:chiskewt}$), we now clarify that $\pi(h)$ goes to zero as $h$ increases assuming that the knots follow a homogeneous Poisson process.
    In the model fitting procedure above (\ref{eq:hier})
  \end{response}

  The proof in Web Appendix C also needs some greater attention to detail. It looks to me as if using defintion (7) and for a fixed radius $h$ then $\bs_1$ and $\bs_2$ need not be in different partitions almost surely, although this may be the case as $h \rightarrow \infty$. Perhaps I am wrong, but either way it would be helpful to have the full proof spelt out to avoid any confusion. \\

  \begin{response}
    \hl{DONE:}
    We have provided a more complete proof that $\lim_{h \rightarrow \infty} \pi(h) = 0$ in \ref{a:proofsamepartition}.
  \end{response}

  \item Section 3.3: As you note, there are several places where you could introduce temporal dependence. Are you able to analyze any theoretical properties of the suggested form, or even how this matches the data? \\

  \begin{response}
    \hl{TODO:}
    Yes, as noted in the response to AE (major comment 5), we have evidence using simulated data that our temporal construction maintains extremal dependence.
    This now appears \hl{where it will appear}.
    Thank you both for the suggestion!
  \end{response}

@@

  \item Section 5: The simulation study needs more details. For example, when fitting datasets (1)--(4) to model (6) (max-stable), were the margins of this estimated or assumed fixed? Also you fit trend terms in some models when the mean is constant, and do not comment on the rationale for this or what happens to the estimates of these parameters (are $\beta_\text{lat}$ and $\beta_\text{long}$ close to 0 and $\beta_\text{int}$ close to 10?)

  Furthermore the range of models simulated from is rather limited; for (4) you could simulate from a range of different max-stable processes (even if you don’t fit these, it might be interesting to see how the skew-t model handles them). \\

  \begin{response}
    \hl{Partly done:}
    We have added clarification for these points in the description of the simulation study.
    The parameters in the marginal distribution for all methods were estimated in a fully-Bayesian manner using MCMC methods.
    The constant mean function was chosen somewhat arbitrarily, but permits a common threshold to apply to all sites.
    Finally, we have also added a 5th design to the simulation study using a Brown-Resnick process with range 1 and smoothness 0.5, and find that the skew-$t$ method performs similarly to the other setting.
    For this new setting, we find that our model performs similarly to the case in setting (4) with some improvement over the max-stable method for lower quantiles (0.90 -- 0.98), and the max-stable method tends to perform better at more extreme quantiles.
  \end{response}

  It would be nice to see alternative model evaluations to the Brier score, or at least perhaps gain some sense of whether there is strong spatial variation in the score. If the model is much better at predicting in some locations than others, then one may want to be wary of using it in some areas\ldots \\

  \begin{response}
    \hl{TODO:}
    We agree that maps of Brier scores would be informative.
    This information could conceptually inform future monitor sites.
    We have now added a map of Brier scores (see Web Figure), which shows \hl{XXXX}.
  \end{response}

  \item Section 6: why do you only use July data? Is this a computational restriction, due to availability of data, or due to particular interest in that month? As you point out, if you used more data then you would be able to say more about the extremal dependence, so this point is rather pertinent. Indeed, although Figure 6 shows that two particular sites close together are relatively strongly dependent, we see nothing about the general picture of $\chi(h)$. I agree this would be difficult to assess with so few data, but it’s not clear whether you have more data available to help assess this (even if you didn’t fit the model to all of them). \\

  \begin{response}
    \hl{TODO:}
    Ozone exhibits strong seasonal patterns, so analyzing a longer series would require additional parameters.
    Additional monitoring data would be easy enough to gather because it is available online.
    The real limitation in our case is the CMAQ data, which we only have for this time period.
  \end{response}
\end{enumerate}

\subsection*{Minor comments}
\hl{Unless otherwise stated, these are done}

\begin{enumerate}[1.]
  \item p.5l.6 $\gamma \rightarrow 1 - \gamma$. \\

  \begin{response}
    This typo has been corrected.
  \end{response}

  \item p.8 l.8 should $w_{t,1}$ etc. be bold? \\

  \begin{response}
    This typo has been corrected.
  \end{response}

  \item p. 8 final line: the phrase ``use a copula'' could be omitted as it seems superfluous and may introduce unnecessary confusion. Giving adequate details on the transformation and dependence structure is sufficient. \\

  \begin{response}
    We have replaced ``use a copula'' with ``use a transformation of a Gaussian random variable'' above (\ref{eq:sigmastar}) and (\ref{eq:zstar}).
  \end{response}

  \item p. 12 final line: you fit the correct model in some of these cases, so is it still difficult to tell whether the parameters converge even in this situation? \\

  \begin{response}
    \hl{I'm going to try to add in something about whether or not the parameters converge for skew-$t$ with 1 knot}
    As with any Bayesian mixture model, the labels of the partitions are arbitrary.
    That is, we could swap the labels of knots 1 and 2, and this would not affect the value of the posterior.
    It would, however, change the values of $z_1$ and $z_2$ making it difficult to study convergence for these parameters.
    However, since the quantities of interest (spatial predictions and probability of extreme events) are defined marginally over the partitioning, label-switching does not affect convergence for these quantities.
  \end{response}

  \item p.13 l.13 and l.15 please give references for these tests \\

  \begin{response}
    These have been added
  \end{response}

  \item p.14 eq.(20): Do you specify the mean of $Y$, or use the covariate specification given in (1)? These don’t look to be the same if $\lambda \neq 0$. \\

  \begin{response}
    Yes, technically the mean of $Y(\bs)$ depends on the shape parameter.
    To match this equation with (\ref{eq:fullmodel}), we now simply specify that $\bX_t(\bs) = [1, \text{CMAQ}_t(\bs)]^\top$
  \end{response}
\end{enumerate}

\newpage
\section*{Response to the comments of the Reviewer 2}
\hl{I've addressed some of these in the updated draft, but not all of them.}

### 2016-06-06 LaTeX/skewt_rev.tex
manuscript changes for revisions.

\pagerange{\pageref{firstpage}--\pageref{lastpage}}

\label{firstpage}

@@

\section{Introduction}\label{s:intro}
% In many climatological applications, researchers are interested in learning about the average behavior of different climate variables (e.g. ozone, temperature, rainfall).
Epidemiological studies have linked air quality to public health concerns regarding morbidity and mortality \citep{Samet2000}.
As a result, the Environmental Protection Agency (EPA) has developed a set of standards to help reduce air pollution thereby improving air quality.
Our study is motivated by an air pollution application where the focus is not on the average behavior, but instead the behavior over a fixed threshold determined by government regulation.
More specifically, we consider the case of compliance for ozone.
A site is said to be in compliance if the fourth highest daily maximum 8-hour concentration averaged over 3 years does not exceed 75 parts per billion (ppb).
Figure \ref{fig:ozone-10jul} shows the ozone levels from July 10, 2005, at 1089 stations across the United States.
We see a large area above the compliance level in the midwest covering Ohio, Indiana, Illinois, and parts of the surrounding states.

\begin{figure}[h!tbp]
  \centering
  \includegraphics[width=0.75\linewidth]{plots/ozone-10jul-us.pdf}
  \caption{Ozone values (ppb) on July 10, 2005}
  \label{fig:ozone-10jul}
\end{figure}

A spatial model for threshold exceedances warrants special consideration and standard spatial methods are likely to perform poorly.
First, because we are interested only in high values, we want to ``let the tail speak for itself''.
That is, if we fit a model to the entire data set, low-to-moderate values would influence the fit of the overall model.
As there are more of these values, they can unduly influence the distribution at the higher levels about which we are interested.
Our inference method will only use data which exceed a threshold, and will impute data below the threshold, thereby tailoring the fit to the levels of interest.
Second, likelihood-based spatial modeling typically assumes a Gaussian process, which is appropriate when mean behavior is of interest.
However, the Gaussian distribution is light-tailed and symmetric, and therefore may be inappropriate for modeling data which does not share this tail behavior.
Third, we aim to capture the dependence structure when ozone is at high levels, and dependence at these levels may not be well-represented by covariances which focus again on mean behavior.
Asymptotic dependence/independence (see Section \ref{s:extdep}) are notions which describe how two random variables' probability of simultaneous exceedance of an extreme threshold behaves as one increases the threshold.
The Gaussian distribution always exhibits asymptotic independence, except in the case of perfect dependence, thus is an inappropriate model for data which exhibits asymptotic dependence.
To allow for more flexibility in the marginal tail and to allow for asymptotic dependence, the skew-$t$ distribution forms the basis for our model.

@@

We propose a new spatiotemporal threshold exceedance model based on the skew-$t$ process \citep{Padoan2011}.
Our model is a threshold exceedance model for the multivariate skew-$t$ distribution for a fixed threshold.
In this setting, we describe the threshold as fixed because it is specified in advance by regulatory compliance.
This differs from the more traditional extremes literature where a threshold is selected to be the value beyond which an extremal model is appropriate for the data.
We use a skew-$t$ distribution because of its flexibility to model asymmetry and heavy-tailed data with the aim of predicting the probability of exceeding a high fixed threshold at an unobserved location.

@@

The paper is organized as follows.
Section \ref{s:spatialskew} is a brief review of the spatial skew-$t$ process.
In Section \ref{s:spatial}, we build upon the traditional skew-$t$ process by incorporating censoring to focus on tails, partitioning to remove long-range asymptotic dependence, and extending the model to space-time data.
The computing is described in Section \ref{s:hier}.
In Section \ref{s:simstudy}, we present a simulation study that examines the predictive capabilities of this model compared to Gaussian and max-stable methods.
We then compare our method to Gaussian and max-stable methods with a data analysis of ozone measurements from 800 sites throughout the US in Section \ref{s:analysis}.
The final section provides brief discussion and direction for future research.

@@

\section{Spatial skew processes}\label{s:spatialskew}
The skew-elliptical family of distributions provides models that are mathematically tractable while introducing a slant parameter to account for asymmetric data \citep{Azzalini2014}.
A brief review of the additive process by which a skew-$t$ process is created is given here.

\subsection{Skew-$t$ process} \label{s:skewt}
Let $Y(\bs)$ be the observation at spatial location $\bs$ in a spatial domain of interest $\calD \in \calR^2$.
The spatial skew-$t$ process can be written
\begin{align}
  Y(\bs) = \bX(\bs)^\prime \bbeta + \lambda \sigma |z| + \sigma v(\bs) \label{eq:fullmodel}
\end{align}
where $\bX(\bs)$ is a set of spatial covariates at site $\bs$, $\bbeta$ is the vector of regression parameters, $\lambda \in \calR$ is a parameter controlling skew, $z \sim N(0, b)$, $\sigma^2 \sim \text{IG}(a / 2, a / 2)$ is random scale parameter, IG is the distribution function of an inverse gamma random variable, and $v(\bs)$ is a spatial Gaussian process with mean zero, variance $b^2$, and a positive definite correlation function $\rho(\bs_1, \bs_2)$.
Although any positive definite correlation function could be used, we choose to use the stationary isotropic \Matern correlation with
\begin{align}
  \rho(h) = (1 - \gamma) I(h = 0) + \gamma \frac{ 1 }{ \Gamma(\nu) 2^{ \nu - 1}} \left( \sqrt{2\nu} \frac{ h }{ \varphi } \right)^{\nu} K_{\nu} \left( \sqrt{2\nu} \frac{ h }{ \varphi } \right) \label{eq:matern}
\end{align}
where $\varphi$ is the spatial range, $\nu$ is the smoothness, $\gamma$ is the proportion of variance accounted for by the spatial variation, $K_\nu$ is a modified Bessel function of the second kind, and $h = || \bs_1 - \bs_2 ||$ is the distance between sites $\bs_1$ and $\bs_2$.

For a finite collection of locations $\bs_1, \ldots, \bs_n$, denote the vector of observations $\bY = [Y(\bs_1), \ldots, Y(\bs_n)]^\prime$.
After marginalizing over both $z$ and $\sigma$,
\begin{align}
  \bY \sim \text{ST}_n(\bX \bbeta, \bOmega, \balpha, 2a),
\end{align}
that is, $\bY$ follows an $n$-dimensional skew-$t$ distribution with location $\bX \bbeta$, variance matrix $\bOmega$, slant parameters $\balpha$ and degrees of freedom $2a$, where $\bX = [\bX(\bs_1)^\prime, \ldots, \bX(\bs_n)^\prime]$, $\bOmega = \bomega \bar{\bOmega} \bomega$, $\bomega = \text{diag}\left(\frac{1}{ \sqrt{ab}}, \ldots, \frac{1}{\sqrt{ab}}\right)$, $\bar{\bOmega} = (\bSigma + \lambda^2 \bOne \bOne^\prime$), $\balpha = \lambda (1 + \lambda^2 \bOne^\prime \bSigma^{-1} \bOne)^{-1/2} \bOne^\prime \bSigma^{-1}$, and $\bSigma$ is the positive definite correlation matrix which is obtained from $\rho(h)$.
This process is desirable because of its flexible tail that is controlled by the skewness parameter $\lambda$ and degrees of freedom $2a$.
Furthermore, the marginal distributions at each location also follow a univariate skew-$t$ distribution \citep{Azzalini2014}.

@@

\subsection{Extremal dependence}\label{s:extdep}
Our interest lies in spatial dependence in the tail of the skew-$t$ process.
One measure of extremal dependence is the $\chi$ statistic \citep{Coles1999}.
For a stationary and isotropic spatial process, the $\chi$ statistic for locations $\bs_1$ and $\bs_2$ separated by distance $h = || \bs_1 - \bs_2 ||$ with identical marginal distributions is
\begin{align}
  \chi(h) = \lim_{c \rightarrow c^*} \Pr[Y(\bs_1) > c | Y(\bs_2) > c]
\end{align}
where $c^*$ is the upper limit of the support of $Y$.
For the skew-$t$ distribution, $c^* = \infty$.
If $\chi(h) = 0$, then observations are asymptotically independent at distance $h$.
For Gaussian processes, $\chi(h) = 0$ regardless of the distance $h$, so they are not suitable for modeling asymptotically dependent extremes.
Unlike the Gaussian process, the skew-$t$ process is asymptotically dependent (the explicit expression for $\chi(h)$ is given in \ref{a:skewt}).
However, one problem with the spatial skew-$t$ process is that $\lim_{h \rightarrow \infty} \chi(h) > 0$.
This occurs because all observations, both near and far, share the same $z$ and $\sigma$ terms.
Therefore, this long-range dependence feature of the skew-$t$ process is not ideal for spatial analysis of large geographic regions where we expect only local spatial dependence.
We propose a solution to this in Section \ref{s:part}.

>>>>

\pagerange{\pageref{stfirstpage}--\pageref{stlastpage}}

\label{stfirstpage}

@@

\section{Introduction}\label{sts:intro}
% In many climatological applications, researchers are interested in learning about the average behavior of different climate variables (e.g. ozone, temperature, rainfall).
Epidemiological studies have linked air quality to public health concerns regarding morbidity and mortality \citep{Samet2000}.
As a result, the Environmental Protection Agency (EPA) has developed a set of standards to help reduce air pollution thereby improving air quality.
Our study is motivated by an air pollution application where the focus is not on the average behavior, but instead the behavior over a fixed threshold determined by government regulation.
More specifically, we consider the case of compliance for ozone.
A site is said to be in compliance if the fourth highest daily maximum 8-hour concentration averaged over 3 years does not exceed 75 parts per billion (ppb).
\fref{stfig:ozone-10jul} shows the ozone levels from July 10, 2005, at 1089 stations across the United States.
We see a large area above the compliance level in the midwest covering Ohio, Indiana, Illinois, and parts of the surrounding states.
We analyze these data with the goals of spatial prediction for unmonitored locations and to map the probability of extreme events.

\begin{figure}[h!tbp]
  \centering
  \includegraphics[width=0.75\linewidth]{plots/ozone-10jul-us.pdf}
  \caption{Ozone values (ppb) on July 10, 2005}
  \label{stfig:ozone-10jul}
\end{figure}

A spatial model for threshold exceedances warrants special consideration and standard spatial methods are likely to perform poorly.
First, because we are interested only in high values, we want to ``let the tail speak for itself''.
That is, if we fit a model to the entire data set, low-to-moderate values would influence the fit of the overall model.
As there are more of these values, they can unduly influence the distribution at the higher levels about which we are interested.
Our inference method will only use data which exceed a threshold, and will impute data below the threshold, thereby tailoring the fit to the levels of interest.
Second, likelihood-based spatial modeling typically assumes a Gaussian process, which is appropriate when mean behavior is of interest.
However, the Gaussian distribution is light-tailed and symmetric, and therefore may be inappropriate for modeling data which does not share this tail behavior.
Third, we aim to capture the dependence structure when ozone is at high levels, and dependence at these levels may not be well-represented by covariances which focus again on mean behavior.
Asymptotic dependence/independence (see \sref{sts:extdep}) are notions which describe how two random variables' probability of simultaneous exceedance of an extreme threshold behaves as one increases the threshold.
The Gaussian distribution always exhibits asymptotic independence, except in the case of perfect dependence, thus is an inappropriate model for data which exhibits asymptotic dependence.
To allow for more flexibility in the marginal tail and to allow for asymptotic dependence, the skew-$t$ distribution forms the basis for our model.

@@

We propose a new spatiotemporal threshold exceedance model based on the skew-$t$ process \citep{Padoan2011}.
Our model is a threshold exceedance model for the multivariate skew-$t$ distribution for a fixed threshold.
In this setting, we describe the threshold as fixed because it is specified in advance by regulatory compliance.
This differs from the more traditional extremes literature where a threshold is selected to be the value beyond which an extremal model is appropriate for the data.
We use a skew-$t$ distribution because of its flexibility to model asymmetry and heavy-tailed data with the aim of predicting the probability of exceeding a high fixed threshold at an unobserved location.
\hl{Need to add in more references here to skew-$t$ used in a spatial setting.}

@@

The paper is organized as follows.
\sref{sts:spatialskew} is a brief review of the spatial skew-$t$ process.
In \sref{sts:spatial}, we build upon the traditional skew-$t$ process by incorporating censoring to focus on tails, partitioning to remove long-range asymptotic dependence, and extending the model to space-time data.
The computing is described in \sref{sts:hier}.
In \sref{sts:simstudy}, we present a simulation study that examines the predictive capabilities of this model compared to Gaussian and max-stable methods.
We then compare our method to Gaussian and max-stable methods with a data analysis of ozone measurements from 800 sites throughout the US in \sref{sts:analysis}.
The final section provides brief discussion and direction for future research.

@@

\section{Spatial skew processes}\label{sts:spatialskew}
The skew-elliptical family of distributions provides models that are mathematically tractable while introducing a slant parameter to account for asymmetric data.
A brief review of the additive process (\citealp{Azzalini2003}; \citealp[p. 129]{Azzalini2014}; \citealp{Beranger2016}) by which a skew-$t$ process is created is given here.

\subsection{Skew-$t$ process} \label{sts:skewt}
Let $Y(\bs)$ be a spatial process defined for spatial location $\bs$ in a spatial domain of interest $\calD \in \calR^2$.
The spatial skew-$t$ process can be written
\begin{align}
  Y(\bs) = \bX(\bs)^\top \bbeta + \lambda \sigma |z| + \sigma v(\bs) \label{steq:fullmodel}
\end{align}
$\bX(\bs)$ is the observed covariate vector at site $\bs$, $\bbeta$ is the $p$-vector of regression parameters, $\lambda \in \calR$ is a parameter controlling skew, $z \sim N(0, 1)$, $\sigma^2 \sim \text{IG}(a / 2, b)$ is random scale parameter, IG is the distribution function of an inverse gamma random variable, $a$ is the degrees of freedom, $b$ controls the precision of the process, and $v(\bs)$ is a spatial Gaussian process with mean zero, variance one, and a positive definite correlation function $\text{Cor} \left[Y(\bs_1), Y(\bs_2)\right] = \rho(\bs_1, \bs_2)$.
Although any positive definite correlation function could be used, we choose to use the stationary isotropic \Matern correlation with
\begin{align}
  \rho(h) = (1 - \gamma) I(h = 0) + \gamma \frac{ 1 }{ \Gamma(\nu) 2^{ \nu - 1}} \left( \sqrt{2\nu} \frac{ h }{ \varphi } \right)^{\nu} K_{\nu} \left( \sqrt{2\nu} \frac{ h }{ \varphi } \right) \label{steq:matern}
\end{align}
where $\varphi$ is the spatial range, $\nu$ is the smoothness, $\gamma$ is the proportion of variance accounted for by the spatial variation, $K_\nu$ is a modified Bessel function of the second kind, and $h = || \bs_1 - \bs_2 ||$ is the Euclidean distance between sites $\bs_1$ and $\bs_2$.

For a finite collection of locations $\bs_1, \ldots, \bs_n$, denote the vector of observations $\bY = [Y(\bs_1), \ldots, Y(\bs_n)]^\top$.
After marginalizing over both $z$ and $\sigma$, using the notation from \citet[p. 176]{Azzalini2014},
\begin{align} \label{steq:stazzalini}
  \bY \sim \text{ST}_n(\bX \bbeta, \bOmega, \balpha, a),
\end{align}
that is, $\bY$ follows an $n$-dimensional skew-$t$ distribution with location $\bX \bbeta \in \calR^n$, variance matrix $\bOmega_{n \times n}$, $\balpha \in \calR^n$ slant parameters, degrees of freedom $a$, where $\bX_{n \times p} = [\bX(\bs_1)^\top, \ldots, \bX(\bs_n)^\top]$,
$\bX(\bs_i), i = 1, \ldots, n$, are observed covariates at each site,
$\bOmega_{n \times n} = \bomega \bar{\bOmega} \bomega$,
$\bar{\bOmega}_{n \times n} = \frac{1}{1 + \lambda^2}(\bSigma + \lambda^2 \bOne \bOne^\top)$,
$\bomega_{n \times n} = \text{diag}\left(\sqrt{\frac{a(1 + \lambda^2)}{ b }}, \ldots, \sqrt{\frac{a(1 + \lambda^2)}{ b }} \right)$,
$\balpha = \lambda (1 + \lambda^2)^{1 / 2} (1 + \lambda^2 \bOne^\top \bSigma^{-1} \bOne)^{-1/2} \bSigma^{-1} \bOne$, and $\bSigma_{n \times n}$ is the positive definite correlation matrix which is obtained from $\rho(h)$.
This process is desirable because of its flexible tail that is controlled by the skewness parameter $\lambda$ and degrees of freedom $a$.
Furthermore, the marginal distributions at each location also follow a univariate skew-$t$ distribution \citep{Azzalini2014}.
For comparisons with other parameterizations, please see \aref{sta:otherparams}.

@@

\subsection{Extremal dependence}\label{sts:extdep}
Our interest lies in spatial dependence in the tail of the skew-$t$ process.
One measure of extremal dependence is the $\chi$ statistic \citep{Coles1999}.
For a stationary and isotropic spatial process, the $\chi$ statistic for locations $\bs_1$ and $\bs_2$ separated by distance $h = || \bs_1 - \bs_2 ||$ with identical marginal distributions is
\begin{align} \label{steq:chih}
  \chi(h) = \lim_{c \rightarrow c^*} \Pr[Y(\bs_1) > c | Y(\bs_2) > c]
\end{align}
where $c^*$ is the upper limit of the support of $Y$.
For the skew-$t$ distribution, $c^* = \infty$.
If $\chi(h) = 0$, then observations are asymptotically independent at distance $h$.
For Gaussian processes, $\chi(h) = 0$ regardless of the distance $h$, so they are not suitable for modeling asymptotically dependent extremes.
Unlike the Gaussian process, the skew-$t$ process is asymptotically dependent (the explicit expression for $\chi(h)$ is given in \aref{sta:skewt}).
However, one problem with the spatial skew-$t$ process is that $\lim_{h \rightarrow \infty} \chi(h) > 0$.
This occurs because all observations, both near and far, share the same $z$ and $\sigma$ terms.
Therefore, this long-range dependence feature of the skew-$t$ process is not ideal for spatial analysis of large geographic regions where we expect only local spatial dependence.
We propose a solution to this in \sref{sts:part}.
